(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation?

### 2015-03-11 ms.tex
cleaning up more text

\newcommand{\Nfp}{4}
\newcommand{\Nvalidated}{22}
\newcommand{\Nlimbo}{10} %adds to 36?  good.

@@

\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving
Earth-like Insolation?)}

\newcommand{\caltech}{1}
\newcommand{\cfa}{2}
\newcommand{\nyu}{3}
\newcommand{\princeton}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\jcpa}{7}
\newcommand{\texas}{8}
\newcommand{\hjs}{9}

\author{%
% The Heavy Lifters
Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
Daniel~Foreman-Mackey\altaffilmark{\nyu},
Timothy~D.~Morton\altaffilmark{\princeton},
% The Benefactors
John~Asher~Johnson\altaffilmark{\cfa},
David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
% The Observers
% (ranked by integration time x collecting area)
Brendan~P.~Bowler\altaffilmark{\caltech, \jcpa},
David~W.~Latham\altaffilmark{\cfa},
Allyson~Bieryla\altaffilmark{\cfa},
Andrew~W.~Mann\altaffilmark{\texas, \hjs},
And Any TRES Team Members We Should Add
}

@@

In this paper, we present stellar and planetary parameters for each system.
Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
level. We also are able to confirm \anytodo{Number} of these systems as false positives.

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties.
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}.
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit,
and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
These data are reported in Table 1.

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.  
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12}
for each host star conditioned on the observed 
photometric properties as presented in \ref{Table:photometry}, with 
the exception of the W4 band, which we leave out this analysis due to 
its unreliability.

@@

\anytodo{Is this paragraph necessary anymore?}
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included.
However, at the low-mass end including the WISE data systematically increases the
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552
(\textsection\ref{Spexobs}) suggest the derived photometric properties better
represent the true physical parameters when the WISE data is included.

\btmtodo{Show plot}

@@

For EPIC 201295312, the transit depth is significantly shallower than
the maximum false positive depth, so we cannot immediately
reject the hypothesis that the transit is actually a false positive
induced by a background eclipsing binary. \anytodo{Can we place limits
on this possibility from the lack of a centroid shift?}

@@

\btmtodo{Method}

\btmtodo{Plots showing POSS observations.}

For these targets, we can extend our contrast curves to zero
present-day orbital separation and rule out the possibility that
these transit events are caused by background eclipsing binaries.
By combining present-day seeing-limited photometric survey data,
adaptive optics imaging, and archival photometry, the only stellar companions
we would not detect would be those that are gravitationally bound to the target
star and positioned in their orbits so that their projected separation is
smaller than the diffraction limit of the P200 telescope.
Such an alignment would require the orbital inclination of the binary to be
nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
While we cannot fully rule out this possibility, such an alignment is unlikely
to occur, and highly unlikely to cause enough dilution to call the planetary
nature of these signals into question.

@@

\subsection{False Positive Rates (and confirmations?)}
This is Tim.

@@

\subsection{EPIC 201465501?}
Is this a subsection? It's a star with a mass of ~0.2 Msun and a candidate with
a period of 18 days. I suppose it depends on the FPP.

\subsection{An Instrumental False Positive}

EPIC 201555883 was originally listed in \paperit\ as a planet candidate.
After submission of that work, this object of interest was identified as
having a transit ephemeris consistent with that of EPIC 201569483,
which we identify as a likely eclipsing binary due to the observed transit
depth \anytodo{Right? Right?  Can this be more quantitative?  Are these two stars 
close to one another?  How bright is  the purported parent? Are they 
On/near the same CCD column?  FPP gives this a pass, so we 
need to be clear about this.}.
We conclude the observed transit signal from EPIC 201555883 is likely the result
of an instrumental artifact.

Such effects are not uncommon in \kep\ data.
\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
ephemerides between candidates.
In that paper, the authors limited their search to candidates within $20\arcsec$ of other
objects of interest.
\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and
outlining four physical reasons why these anomalies may occur.
While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
explained by any one of the effects described by \citet{Coughlin14} alone.
This artifact should be carefully studied in the future, as it may help illuminate other
potential detector artifacts, both in \kep\ and \KT\ data.

@@

We have presented stellar parameters for all planet candidates systems observed by
\paperit, confirming \btmtodo{Nconfirm} of the 36 candidates as bona fide planets and
\btmtodo{NFP} as bona fide false positives.

@@

\acknowledgements
We thank Eric Agol (UW), Dan Huber (Sydney) [and Other People] for conversations and
suggestions which improved the quality of this manuscript.

@@

{\it Facilities:} \facility{Kepler}, \btmtodo{More...}

>>>>

\newcommand{\Nfp}{4}
\newcommand{\Nvalidated}{21}
\newcommand{\Nlimbo}{11} %adds to 36?  good.

@@

\title{(Working Title) Stellar and Planetary Properties of \KT\ \Ci\
Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving
Earth-like Insolation?}

\newcommand{\caltech}{1}
\newcommand{\cfa}{2}
\newcommand{\nyu}{4}
\newcommand{\princeton}{3}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\jcpa}{7}
\newcommand{\texas}{8}
\newcommand{\hjs}{9}

\author{%
% The Heavy Lifters
Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
Timothy~D.~Morton\altaffilmark{\princeton},
Daniel~Foreman-Mackey\altaffilmark{\nyu},
% The Benefactors
John~Asher~Johnson\altaffilmark{\cfa},
David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
% The Observers
% (ranked by integration time x collecting area)
Brendan~P.~Bowler\altaffilmark{\caltech, \jcpa},
David~W.~Latham\altaffilmark{\cfa},
Allyson~Bieryla\altaffilmark{\cfa},
Andrew~W.~Mann\altaffilmark{\texas, \hjs},
And Any TRES Team Members We Should Add
}

@@

In this paper, we present stellar and planetary parameters for each system.
Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm
\Nvalidated\ of these systems as transiting planets at the 99\% confidence
level. We also are able to confirm \Nfp\ of these systems as false positives.

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties.
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}.
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
\citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit,
and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
order of magnitude larger than those in $W1-W3$, so we neglect $W4$.
These data are reported in Table 1.

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.  
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12},
an implementation of the affine-invariant ensemble sampler of 
\citet{Goodman10}
for each host star conditioned on the observed 
photometric properties as presented in \ref{Table:photometry}, with 
the exception of the W4 band, which we leave out this analysis due to 
its unreliability.

@@

@@

For EPIC 201295312, the transit depth is significantly shallower than
the maximum false positive depth, so we cannot immediately
reject the hypothesis that the transit is actually a false positive
induced by a background eclipsing binary. 
However, from the transit shape alone we can place a FPP of this
system of $1.1 \times 10^{-4}$.

@@

For all targets with AO, we can confirm the planetary nature of the signal 
without this extra step, but we include it for EPIC 201912552 for 
completeness, considering thee additional follow-up this target may warrant.
We download data from the POSS I and II surveys, which imaged
EPIC 201912552 in 1955 and 1989, respectively. 
This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in RA and 
$-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8.35\arcsec$ 
since the POSS I data were collected.
As shown in Figure \ref{fig:archival}, we do not detect any targets at the 
present-day location of EPIC 201912552 in either of the POSS surveys.

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 1.5cm 0 1.5cm, clip=true]{f3}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed 
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view.}
\label{fig:archival}
\end{figure*}

For this target, we can extend our contrast curves to zero
present-day orbital separation and rule out the possibility that
these transit events are caused by a background eclipsing binary.
By combining present-day seeing-limited photometric survey data,
adaptive optics imaging, and archival photometry, the only stellar companions
we would not detect would be those that are gravitationally bound to the target
star and positioned in their orbits so that their projected separation is
smaller than the diffraction limit of the P200 telescope.
Such an alignment would require the orbital inclination of the binary to be
nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
While we cannot fully rule out this possibility, such an alignment is unlikely
to occur, and highly unlikely to cause enough dilution to call the planetary
nature of this signal into question.

@@

@@

\subsection{Two Candidates, One Ephemeris}

EPIC 201569483 was originally listed in \paperit\ as a planet candidate.
The transit events have a depth of approximately 7\%.
In this work, we conclude this system is more likely than not a false 
positive, with an FPP of 0.560. 
The most likely scenario is that of an eclipsing binary, which would 
not be surprising given the transit depth.

It was later realized that EPIC 201555883 has a period, time of transit, 
and transit duration consistent with EPIC 201569483. 
Such effects are not uncommon in \kep\ data.
\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
ephemerides between candidates.
In that paper, the authors limited their search to candidates within $20\arcsec$ of other
objects of interest.
\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and
outlining four physical reasons why these anomalies may occur.
As those authors explain, period-matching candidates can be the result of direct PRF 
contamination, antipodal reflection across the Schmidt telescope, CCD crosstalk 
across a \kep\ module, or ``column anomalies'' across one column of the CCD.

EPIC 201555883 is a unique case in that it does not appear to fall under any of these 
cases. It falls on module 23, while EPIC 201569483 is on module 8, neither 180 degrees
away from or on the same column as this candidate. 
Moreover, there is not any evidence of a mechanism that could cause a third star to 
induce both the appearance of a $7\%$ eclipse on one module and an additional 
transit event on a different module.

Formally, our false positive validation scheme gives a FPP of $9.5 \times 10^{-4}$, 
reaching our threshold for planet validation. 
In this case, given the period matching between the two events, we refrain from 
declaring this system a planet. 
However, since we cannot explain how such a false positive would occur as a result
of an instrumental systematic in the \kep\ telescope, we also refrain from declaring 
this target a definite false positive. 
Additional follow-up observations of both targets are clearly warranted to better
understand a possible systematic that has not previously been observed in 
either \kep\ or \KT.

@@

We have presented stellar parameters for all planet candidates systems observed by
\paperit, validating \Nvalidated\ of the 36 candidates as bona fide planets and
\Nfp\ as bona fide false positives.

@@

\acknowledgements
We thank Eric Agol (UW), Dan Huber (Sydney) and Jeff Coughlin (SETI) for 
conversations and suggestions which improved the quality of this manuscript.

@@

{\it Facilities:} \facility{Kepler},  \facility{PO:Hale (PHARO)}, \facility{FLWO:1.5m},
\facility{IRTF:SpeX}
